## Solutions to Questions

```{r lab3-solutions-data, eval = TRUE, echo = FALSE, message = FALSE, warning = FALSE}
menrot <-read_csv("./data/03-s01/inclass/MentalRotationBehavioralData.csv")
demog <- read_csv("./data/03-s01/inclass/demographics.csv")
``` 

Below you will find the solutions to the questions for the Activities for this chapter. Only look at them after giving the questions a good try and speaking to the tutor about any issues.

### InClass Activities

#### InClass Task 1

```{r Ch3InClassSolT1, eval=FALSE}
library("tidyverse")

menrot <- read_csv("MentalRotationBehavioralData.csv")
demog <- read_csv("demographics.csv")
```

[Return to Task](#Ch3InClassQueT1)

#### InClass Task 2

```{r Ch3InClassSolT2, eval=FALSE}
menrot_angle <- filter(menrot, CorrectResponse == "Correct") %>%
  inner_join(demog, "Participant") %>%
  group_by(Angle) %>% 
  summarise(mean_Resp = mean(Time))

ggplot(data = menrot_angle, aes(x = Angle, y = mean_Resp)) + 
  geom_point() +
  geom_line() +
  coord_cartesian(ylim = c(0, 3500), expand = TRUE)
```

* `coord_cartesian()` is a function that can be used to show certain parts of a figure, controlling the visible X and Y axes. `expand = TRUE` adds a smaller buffer to the numbers you set. If you want to remove this buffer then set `expand = FALSE`.

[Return to Task](#Ch3InClassQueT2)

#### InClass Task 3

```{r Ch3InClassSolT3, eval=FALSE}
menrot_angle_sex <- filter(menrot, CorrectResponse == "Correct") %>%
  inner_join(demog, "Participant") %>%
  group_by(Angle, Sex) %>% 
  summarise(mean_Resp = mean(Time))

ggplot(data = menrot_angle_sex, aes(x = Angle, y = mean_Resp)) + 
  geom_point() +
  geom_line() +
  coord_cartesian(ylim = c(0, 3500), expand = TRUE)
```

[Return to Task](#Ch3InClassQueT3)

#### InClass Task 4

```{r Ch3InClassSolT4, eval=FALSE}
menrot_grouped <- filter(menrot, CorrectResponse == "Correct") %>%
  inner_join(demog, "Participant") %>%
  group_by(Angle, Sex) %>% 
  summarise(mean_Resp = mean(Time))

ggplot(data = menrot_grouped, aes(x = Angle, y = mean_Resp, group = Sex)) + 
  geom_point() +
  geom_line() +
  coord_cartesian(ylim = c(0, 3500), expand = TRUE)
```

[Return to Task](#Ch3InClassQueT4)

#### InClass Task 5

```{r Ch3InClassSolT5, eval=FALSE}
menrot_grouped_color <- filter(menrot, CorrectResponse == "Correct") %>%
  inner_join(demog, "Participant") %>%
  group_by(Angle, Sex) %>% 
  summarise(mean_Resp = mean(Time))

ggplot(data = menrot_grouped_color, aes(x = Angle, y = mean_Resp, group = Sex)) + 
  geom_point(aes(color = Sex)) +
  geom_line() +
  coord_cartesian(ylim = c(0, 3500), expand = TRUE)
```

[Return to Task](#Ch3InClassQueT5)

#### InClass Task 6

```{r Ch3InClassSolT6, eval=FALSE}
menrot_shape_size <- filter(menrot, CorrectResponse == "Correct") %>%
  inner_join(demog, "Participant") %>%
  group_by(Angle, Sex) %>% 
  summarise(mean_Resp = mean(Time))

ggplot(data = menrot_shape_size, aes(x = Angle, y = mean_Resp, group = Sex)) + 
  geom_point(aes(color = Sex, shape = Sex), size = 3) +
  geom_line() +
  coord_cartesian(ylim = c(0, 3500), expand = TRUE)
```

[Return to Task](#Ch3InClassQueT6)

#### InClass Task 7

```{r Ch3InClassSolT7, eval=FALSE}
menrot_lab_theme <- filter(menrot, CorrectResponse == "Correct") %>%
  inner_join(demog, "Participant") %>%
  group_by(Angle, Sex) %>% 
  summarise(mean_Resp = mean(Time))

ggplot(data = menrot_lab_theme, aes(x = Angle, y = mean_Resp, group = Sex)) + 
  geom_point(aes(color = Sex, shape = Sex), size = 3) +
  geom_line() +
  coord_cartesian(ylim = c(0, 3500), expand = TRUE) +
  labs(x = "Angel of Rotation (degrees)", y = "Mean Reaction Time (ms)") +
  theme_bw()
```

[Return to Task](#Ch3InClassQueT7)

#### InClass Task 8

```{r Ch3InClassSolT8-1, fig.cap='Task 8'}
manrot_facet_guide <- filter(menrot, CorrectResponse == "Correct") %>%
  inner_join(demog, "Participant") %>%
  group_by(Angle, Sex) %>% 
  summarise(mean_Resp = mean(Time))

ggplot(data = manrot_facet_guide, aes(x = Angle, y = mean_Resp, group = Sex)) + 
  geom_point(aes(color = Sex, shape = Sex), size = 3) +
  geom_line() +
  coord_cartesian(ylim = c(0, 3500), expand = TRUE) +
  labs(x = "Angel of Rotation (degrees)", y = "Mean Reaction Time (ms)") +
  facet_wrap(~Sex) +
  guides(group = FALSE, color = FALSE, shape = FALSE) +
  theme_bw()
```

* Remembering it is a layer system, we could use the below code to have the lines behind the points.

```{r Ch3InClassSolT8-2, fig.cap='Task 8 Alternative'}
manrot_facet_guide <- filter(menrot, CorrectResponse == "Correct") %>%
  inner_join(demog, "Participant") %>%
  group_by(Angle, Sex) %>% 
  summarise(mean_Resp = mean(Time))

ggplot(data = manrot_facet_guide, aes(x = Angle, y = mean_Resp, group = Sex)) + 
  geom_line() +
  geom_point(aes(color = Sex, shape = Sex), size = 3) +
  coord_cartesian(ylim = c(0, 3500), expand = TRUE) +
  labs(x = "Angel of Rotation (degrees)", y = "Mean Reaction Time (ms)") +
  facet_wrap(~Sex) +
  guides(group = FALSE, color = FALSE, shape = FALSE) +
  theme_bw()
```



[Return to Task](#Ch3InClassQueT8)


<span style="font-size: 22px; font-weight: bold; color: var(--purple);">Chapter Complete!</span>
