---
title: "Psych 2A Ch4: Formative Probability Assignment"
author: "School of Psychology, University of Glasgow"
output: html_document
---

```{r setup, include=FALSE}
set.seed(1409)
library(tidyverse)
knitr::opts_chunk$set(echo = TRUE)
```

# Instructions

Upon opening this assignment .Rmd file within RStudio you will see there is a code chunk for each of the 10 questions. Much as you did in the previous assignments follow the instructions on what to edit in each code chunk. This will often be entering code or a single value and will be based on the skills learnt in the current lab as well as all previous labs.

## Probability Assignment

In the lab you recapped and expanded on your understanding of probability, including a number of `binom` and `norm` functions as well as some more basic ideas on probability. You will need these skills to complete the following assignment so please make sure you have carried out the PreClass and InClass activities before attempting this formative assignment. Remember to follow the instructions and if you get stuck at any point to questions on the forums.

## Before starting let's check

1. This .Rmd file is saved into a folder on your computer that you have access to and you have manually set this folder as your working directory. For assessments we ask that you save it with the format GUID_Level2_Semester1_Lab4.Rmd where GUID is replaced with your GUID. Though this is a formative assessment it may be good practice to do the same here.

**Note:** You should complete the below code chunks by replacing the `NULL` (except the library chunk where the appropriate code should just be entered). Not all answers require coding. On those that do not require code you can enter the answer as either code, mathematical notation, or an actual single value. Pay attention to the number of decimal places required.

# Part 1: Library

There is a good chance that you will need the tidyverse library at some point in this exercise so load it in the code chunk below:

```{r library}
# hint: something to do with library() and tidyverse

```

# Part 2: Basic probability and the binomial distribution 
 
**Background Information:** You are conducting an auditory discrimination experiment in which participants have to listen to a series of sounds and determine whether the sound was human or not. On each trial participants hear one brief sound (100 ms) and must report whether the sound was from a human (coded as 1) or not (coded as 0). The sounds were either: a person, an animal, a vehicle, or a tone, with each type of sound equally likely to appear.

## Question 1

On a single trial, what is the probability that the sound will not be a person? Replace the `NULL` in the t1 code chunk with either mathematical notation or a single value. If entering a single value, give your answer to two decimal places.

``` {r t1}
t1 <- NULL
```

## Question 2

Over a sequence of 4 trials, with one trial for each sound, and sampled with replacement, what is the probability of the following sequence of sounds: animal, animal, vehicle, tone? Replace the `NULL` in the t2 code chunk with either mathematical notation or a single value. If entering a single value, give your answer to three decimal places.

``` {r t2}
t2 <- NULL
```

## Question 3

Over a sequence of four trials, with one trial for each sound, without replacment, what is the probability of the following sequence of sounds: person, tone, animal, person? Replace the NULL in the t3 code chunk with either mathematical notation or a single value.

``` {r t3}
t3 <- NULL
```

## Question 4

Replace the `NULL` below with code, using the appropriate binomial distribution function, to determine the probability of hearing exactly 17 'tone' trials in a sequence of 100 trials. Assume the probability of a tone on any single trial is 1 in 4. Store the output in `t4`. 

``` {r t4}
t4 <- NULL
```

## Question 5

Replace the `NULL` below with code using the appropriate binomial distribution function to determine what is the probability of hearing 30 'vehicle' trials or more in a sequence of 100 trials. Assume the probability of a vehicle trial on any one trial is 1 in 4. Store the output in `t5`. 
**Hint: do we want the upper or lower tails of the distribution?**
``` {r t5}
t5 <- NULL
```

## Question 6

If a block of our experiment contained 100 trials, enter a line of code to run 10000 replications of one block, summing how many living sounds were heard in each replication. Code 1 for living sounds (person/animal) and 0 for non living sounds (vehicle/tone) and assume the probability of a living sound on any given trial is $p = .5$.

``` {r t6}
t6 <- NULL
```

# Part 2: The Normal Distribution

Previously, in Lab 2, we looked at an ageing research project investigating differences in visual processing speed between younger (M = 22 years) and older adults (M = 71 years). One check in this experiment, prior to further analysis, is to make sure that older participants do not show signs of mild cognitive impairment (early symptoms of Alzheimer's disease). To do this, we carry out a battery of cognitive tests to screen for such symptoms. One of the tests is the D2 test of attention which is a target cancellation task (i.e. participants cross out all letter d's with two dashes from a line of letters - see Lab 2 for an example). It is designed to test peoples' selective and sustained attention and visual scanning speed. The results of the test give a single score of Concentration Performance for each participant. The key piece of information for this analysis is that the distributions of D2 test scores are typically normally distributed (`M = 100`, `SD = 10`).  

## Question 7

Replace the `NULL` below with code using the appropriate function to determine the probability that a given participant will have a D2 score of 90 or lower? Store the output in `t7`

``` {r t7}
t7 <- NULL
```

## Question 8

Replace the `NULL` below with code using the appropriate function to determine the probability that a given participant will have a D2 score of 120 or more? Store the output in `t8`

``` {r t8}
t8 <- NULL
```

## Question 9

Replace the `NULL` below with code using the appropriate function(s) to determine what is the difference in scores that cut off the top and bottom 5% of the distribution? Store the output in `t9`

``` {r t9}
t9 <- NULL
```

## Question 10

Finally, if a participant says to you that they are worried because they have heard that their Concentration Performance was in the bottom 2% of scores on the distribution, what is the maximum D2 score that they can have? Replace the `NULL` below with a single value to two decimal places. Do not enter code. Store this in `t10`

``` {r t10}
t10 <- NULL
```

# Finished

Well done, you are finshed! Now you should go check your answers against the solutions at the end of the chapter. You are looking to check that questions looking for a single value have the same answer as you, and that questions asking for code have the same code as you or give the same answer where alternative variations in the code are allowed (e.g. including `lower.tail = TRUE` or not including it as it is default). Remember that a single value is not the same as a coded answer and that spelling matters, `replicate()` is not the same as `replicat()`. Where there are alternative answers, it means that you could have submitted any one of the options as they should all return the same answer. If you have any questions, please post them on the forums!

Lastly, keep in mind the main point about probability, that we are interested in determining the probability of a given value on a distribution! That is what it is all about and is what we will look at more of in Chapter 5.