## InClass Activity 2 (Additional)

In the preclass activity, we focused a lot on basic probability and **binomial distributions**. If you have followed it, and understood it correctly, you should be able to have a go at the following scenario to help deepen your understanding of the binomial distribution. Have a go and see how you get on. Solutions are at the end of the chapter. 

### Return of the Binomial {Ch4InClassQueBinomial}

You design a psychology experiment where you are interested in how quickly people spot faces. Using a standard task you show images of **faces, houses, and noise patterns,** and ask participants to respond to each image by saying **'face'** or **'not face'**. You set the experiment so that, across the whole experiment, the number of images per stimuli type are evenly split (1/3 per type) but they are not necessarily evenly split in any one block. **Each block contains 60 trials**.  

To test your experiment you run 1 block of your experiment and get concerned that you only saw 10 face images. As this is quite a low number out of a total of 60 you think something might be wrong. You decide to create a probability distribution for a given block of your experiment to test the likelihood of seeing a face (coded as 1) versus not seeing a face (coded as 0).

You start off with the code below but it is incomplete. 

```{r binomial-base, eval = FALSE}
blocks_5k <- replicate(n = NULL, 
                       sample(0:1, 
                              size = NULL, 
                              replace = NULL, 
                              c(2/3,1/3)) %>% 
                         sum())
```

1. Copy the code to a script and replace the `NULLs` with the correct value and statement to establish how many different numbers of faces you might see in 1 block of 60 trials, over 5000 replications. Answering the following questions to help you out:
<br>

<span style="font-size: 22px; font-weight: bold; color: var(--green);">Quickfire Questions</span>

* The `n` NULL relates to: `r mcq(c(answer = "Number of Monte Carlo replications", "Number of blocks in the experiment", "Number of trials in the experiment", "Number of faces in the experiment"))`

* The `size` NULL relates to: `r mcq(c("Number of faces in a block", "Number of houses in a block", answer = "Number of trials in a block", "Number of noise patterns in a block"))`

* `replace` should be set to: `r mcq(c(answer = "TRUE","FALSE"))`

`r hide("Explain This - I don't understand these answers")`
```{block, type ="info"}
* `replicate` is how many times you want to run the sample, n = 5000. Monte Carlo replications are their official name.
* The number of trials is the `size`, 60. 
* And in order for the code to work, and to not run out of options, you need to set `replace` as TRUE.

You saw a very similar code in the preclass so be sure to have had a look there. The solution code is shown at the end of the chapter
```
`r unhide()`

`r hide("Portfolio Point - Why the odd weight of probability?")`
```{block, type ="info"}
Note that the values in the `prob` argument (i.e. `c(2/3, 1/3)` ) set probabilities for the two outcomes specified in the first argument (0, 1). So, we are setting a 2/3 probability of 0 (no face), and a 1/3 probability of 1 (face). Why? Remember that in this instance you have three different stimuli (face, house and noise) and therefore we have a greater chance of not seeing a face in the experiment (i.e. you see a house or noise) than seeing a face in the experiment. You need to remember when using `sample` (`?sample`) to set the probability appropriately or you will end up with an incorrect calculation.
```
`r unhide()`
<br>

2. If you completed the above task correctly, your `blocks_5k` code has created 5000 values where each value represents the number of faces you 'saw' in each individual replication (i.e. block) of 60 trials - like the number of heads you saw in 10 flips. If your code has worked, then running the chunk below should produce a probability distribution of your data. Run it and see. If not, something has gone wrong in your code above; debug or compare you code to the solution at the end of the chapter.  

```{r 5k-plot, include = TRUE, eval = FALSE}
data5k <- tibble(faces_per_block = blocks_5k) %>% 
  count(faces_per_block) %>%
  mutate(p = n / 5000)
ggplot(data5k, aes(faces_per_block, p)) + 
  geom_col() + 
  theme_light()
```

If you view `data5k`, you will now see three columns: 
```{r 5k-tibble, echo=FALSE, include = FALSE}
set.seed(1409)

blocks_5k <- replicate(n = 5000, 
                       sample(0:1,
                              size = 60, 
                              replace = TRUE, 
                              c(2/3,1/3)) %>% sum())

data5k <- tibble(faces_per_block = blocks_5k) %>% 
  count(faces_per_block) %>%
  mutate(p = n / 5000)
```

1. `faces_per_block` tells you all the number of face trials seen in a block of 60 trials. Note that it does not run from 0 to 60. 
2. `n` tells you the number of blocks in which the corresponding number of face trials appeared, e.g. in `r filter(data5k, faces_per_block == 15) %>% pull(n)` blocks there were 15 face trials. (Remember this is sampled data so your values may be different!). 
3. `p` tells you the probability of the corresponding number of `faces_per_block`.

From your `data5k` tibble, what was the probability of seeing only 10 faces in a block? Ours was **`r filter(data5k, faces_per_block == 10) %>% pull(p) %>% round(3)`** but remember that we are using a limited number of replications here so our numbers will vary from yours. To find this value you can use `View()` or `glimpse()` on `data5k`.
<br>

<span style="font-size: 22px; font-weight: bold; color: var(--pink);">Group Discussion Point</span>

Discuss in your groups the following questions:

1. If the probability of seeing only 10 faces was approximately p = `r filter(data5k, faces_per_block == 10) %>% pull(p) %>% round(3)`, what does that say about whether our experiment is coded correctly or not?

2. We only have data for `r dim(data5k)[1]` potential different number of face trials within a block. Why does this value not stretch from 0 to 60, or at least have more potential values than `r dim(data5k)[1]`?

`r hide("Portfolio Point - What does it say about your experimental design?")`
```{block, type ="info"}
On the first point, it says that the probability of having a block with only 10 faces is pretty unlikely - it has only a small probability. However, it is still possible. Does that say there is an error in your code? Not necessarily as it is possible you just happened to get a block with only 10 faces. Despite it being a low probability it is not impossible. What it might say, however, is that if this is something that concerns you, this potentially low number of faces in a block, then you need to think about the overall design of your experiment and consider having an equal weighting of stimuli in each block.

On the second point, you need to think about the width of the distribution. The probability of a face is 1/3 or p = .33. If there are 60 trials per block then that works out, on average, at approx 20 faces per block . The further you move away from that average, 20, the less probable it is to see that number of faces. E.g. 10 faces had a very low probability as will 30 faces. 40 faces will have almost no probability whatsoever. In only 5000 trials not all values will be represented.
```
`r unhide()`  
<br> 
<span style="font-size: 22px; font-weight: bold; color: var(--green);">Quickfire Questions</span>

* Using the appropriate `binom()` function, to three decimal places, type in the actual probability of exactly 10 faces in 60 trials: `r fitb(c("0.002",".002"), width = 8, ignore_ws = TRUE)`

* Using the appropriate `binom()` function, to three decimal places, type in the actual probability of seeing more than, but not including, 25 faces in a block of 60 trials? `r fitb(c("0.068",".068"), width = 8, ignore_ws = TRUE)` 

* Using the appropriate `binom()` function, enter the number of faces needed in a block of 60 trials that would cut off a lower tail probability of .05.`r fitb(c("14"), width = 8, ignore_ws = TRUE)`

`r hide("Helpful Hint")`
```{block, type ="info"}
1. You are looking for the probability of one specific value of faces appearing, i.e. 10 faces in a total of 60 trials. You are not looking for the cumulative probability or a range of values. What does this tell you about the apporpriate `binom()` function you require? Also, in the `sample` function, we created a vector of probability dependent on the appearance of both faces and other stimuli. However, for the `binom()` function, you need to include only the probability of faces appearing - $\frac{1}{3}$. 

2. You are looking for the cumulative probability for seeing more than but not including 25 faces in a block of 60 trials. What does this tell you about the apporpriate `binom()` function you require? Remember to set an appropriate call for `lower.tail`!

3. The probability level has been provided for you (5% 0r .05). With this you are looking to find the cutoff value for this tail. What does this tell you about the appropriate `binom()` function you require? If you are looking for the probability of values at or below this cutoff, is `lower.tail` set to TRUE or FALSE?
```
`r unhide()` 

`r hide("Explain This - I don't get these answers")`
```{block, type ="info"}
1. The answer would be .002 as you require the density, `dbinom()`, of 10 faces out of a possible 60 given a probability of 1/3. The appropriate code is as follows:

**Code:** `dbinom(10, 60, 1/3)`

2. The answer would be .068 as you require the cumulative probability, `pbinom()`, of more than 25 faces out of 60 given a probability of 1/3. As it is more than 25, setting 25 with `lower.tail` set as FALSE will give you 26 and above (remember this is a binomial distribution, so where you set your cut-off is very important). The appropriate code is as follows:

**Code:** `pbinom(25, 60, 1/3, lower.tail = FALSE)`

3. The answer would be 14 using the `qbinom()` function based on wanting to maintain 5% probability of faces in 60 trials. The appropriate code is as follows:

**Code:** `qbinom(.05, 60, 1/3)`
```
`r unhide()`
<br>
<span style="font-size: 22px; font-weight: bold; color: var(--blue);">Job Done - Activity Complete!</span>

Well done on completing this activty! Once you have completed the main body inclass assignment on the Normal Distribution, you should be ready to complete the assignment for this lab. Good luck and remember to refer back to the codes and questions in this lab and the preclass if you get stuck!.
