## Solutions to Questions

```{r lab12-solutions-setup, echo = FALSE, message=FALSE, warning=FALSE}
dmx <- tibble(sub_id = 1:9,
              i = rep(1:3, each = 3),
              j = rep(1:3, times = 3),
              typos = c(111, 102, 111, 
                    89, 127, 90,
                    97, 85, 88),
              sound = rep(c("cafe", "jazz", "silence"), each = 3)) %>%
  mutate(mu = mean(typos)) %>%
  group_by(i) %>%
  mutate(Ai = mean(typos) - mu) %>%
  ungroup() %>%
  mutate(err = typos - (mu + Ai))

dat_ss <- dmx %>% 
  summarise(total = sum(typos^2),
            ss_mu = sum(mu^2),
            ss_sound = sum(Ai^2),
            ss_err = sum(err^2))
```

Below you will find the solutions to the questions for the Activities for this chapter. Only look at them after giving the questions a good try and speaking to the tutor about any issues.

### InClass Activities

#### InClass Task 1 

**Question 1**

* $SS_{corrected\ total} = SS_{total} - SS_{\mu}$
* $SS_{total}$ = `r as.integer(dat_ss[["total"]])`
* $SS_{\mu}$ = `r as.integer(dat_ss[["ss_mu"]])`
* $SS_{corrected\ total}$ = `r as.integer(dat_ss[["total"]])` - `r as.integer(dat_ss[["ss_mu"]])` = `r as.integer(dat_ss[["total"]]) - as.integer(dat_ss[["ss_mu"]])`

**Question 2**

* $SS_{sound}$ = `r as.integer(dat_ss[["ss_sound"]])`
* $SS_{corrected\ total}$ = `r as.integer(dat_ss[["total"]]) - as.integer(dat_ss[["ss_mu"]])`
* $SS_{sound} / SS_{corrected\ total}$ = `r as.integer(dat_ss[["ss_sound"]])` / `r as.integer(dat_ss[["total"]]) - as.integer(dat_ss[["ss_mu"]])` = `r round(as.integer(dat_ss[["ss_sound"]]) / (as.integer(dat_ss[["total"]]) - as.integer(dat_ss[["ss_mu"]])),2)`
    
**Question 3**

* $SS_{err}$ = `r as.integer(dat_ss[["ss_err"]])`
* $SS_{corrected\ total}$ = `r as.integer(dat_ss[["total"]]) - as.integer(dat_ss[["ss_mu"]])`
* $SS_{err} / SS_{corrected\ total}$ = `r as.integer(dat_ss[["ss_err"]])` / `r as.integer(dat_ss[["total"]]) - as.integer(dat_ss[["ss_mu"]])` = `r round(as.integer(dat_ss[["ss_err"]]) / (as.integer(dat_ss[["total"]]) - as.integer(dat_ss[["ss_mu"]])),2)`

[Return to Task](#Ch12InClassQueT1)

#### InClass Task 2

**Question 1**

$\mu_{cafe} = \mu_{jazz} = \mu_{silence}$

**Question 2**

* k = number of conditions, so: 

df = k - 1 = 3 - 1 = 2

**Question 3**

* N = 9, and $dfA_{i}$ = 2, so

df = 9 - 2 - 1 = 6
    
**Question 4**

* The factor df = 2

```{r ms_a}
ms_a <- dat_ss[["ss_sound"]] / 2L
```

* Giving $MS_{A}$ = `r ms_a`

**Question 5**

* The residual df = 6

```{r ms_err}
ms_err <- dat_ss[["ss_err"]] / 6L
```

* Giving $MS_{S(A)}$ = `r ms_err`

[Return to Task](#Ch12InClassQueT2)

#### InClass Task 3

**Question 1**

```{r fratio}
f_obs <- ms_a / ms_err
```

* Giving a F-value of F = `r round(f_obs,3)` when rounded to three decimal places.

**Question 2**

The red line should be about F = 5.143, meaning that that is the minimum value of F, for those dfs, considered to be statistically significant at $\alpha = .05$

**Question 3**

Reading off the app, the approximate p-value for f_obs is p = .317.  

**Question 4**

As $p$ > $\alpha$ we would retain the null hypothesis that there is no significant effect of group in this study

**Question 5**

This could alternatively calculated using coding as such:

```{r ch12Task3Q5sol, eval=FALSE}
pf(f_obs, 2, 6, lower.tail = FALSE)
```

Which would give a p-value of p = `r pf(f_obs, 2, 6, lower.tail = FALSE) %>% round(3)` and again could be written up as F(2, 6) = `r f_obs %>% round(3)`, p = `r pf(f_obs, 2, 6, lower.tail = FALSE) %>% round(3)`, suggesting no significant effect of ambiance or location on concentration as measured through the number of typos.

[Return to Task](#Ch12InClassQueT3)

#### InClass Task 4

```{r afex-input, warning = FALSE}
dat <- select(dmx, sub_id, typos, sound)

results <- afex::aov_ez(data = dat,
                         dv = "typos",
                         id = "sub_id",
                         type = 3,
                         between = "sound")
```
<br>
And when we look at the output table see:

```{r afex-output2, warning = FALSE, echo=FALSE}
options(knitr.kable.NA = '')


knitr::kable(results$Anova,
             digits = 3,
             caption = "ANOVA output")
```
<br>

From this we can see that the numbers we calculated match up exactly with the values that the function produced - F(2, 6) = 1.41, p = .31. You can also see that there is no significant effect and as such we cannot reject the null hypothesis. 

[Return to Task](#Ch12InClassQueT4)

<span style="font-size: 22px; font-weight: bold; color: var(--purple);">Chapter Complete!</span>
