---
title: "Psych 2B Lab 4 Assignment - Two-Factor ANOVA: Perspective-Taking in Language Comprehension"
author: "School of Psychology, University of Glasgow"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Instructions

In order to complete this assignment you first have to download the assignment .Rmd file which you need to edit for this assignment: titled `GUID_Level2_Semester2_Lab4.Rmd`. This can be downloaded within a zip file from the below link. Once downloaded and unzipped you should create a new folder that you will use as your working directory; put the .Rmd file in that folder and set your working directory to that folder through the drop-down menus at the top. <a href="https://www.psy.gla.ac.uk/~phil/L2Labs_201819/semester_two/lab_04/homework/Level2_Semester2_Lab4_AssignmentFiles.zip", target = "_blank">Download the Assignment .zip file from here</a> or on Moodle.

## Background: Perspective-Taking in Language Comprehension

For this assignment, you will be looking at real data from **Experiment 2** of <a href = "https://www.sciencedirect.com/science/article/pii/S0010027703000647?via%3Dihub", target = "_blank">Keysar, Lin, and Barr (2003)</a>, "Limits on Theory of Mind Use in Adults", **Cognition**, **89**, 29--41. This study used eye-tracking to investigate people's ability to take another's perspective during a kind of communication game. (The data that you will be analysing, while real, did not appear in the original report.)

The communication game that participants played was as follows. Each participant sat at a table opposite a confederate participant (a stooge from the lab who pretended to be a naive participant).  Between the two participants was an upright set of shelves (see figure on Moodle).  The participants played a game in which the real participant was assigned the role of the "matcher" and the confederate the role of the "director".  The director was given a picture with a goal state for the grid, showing how the objects needed to be arranged.  However, the director was not allowed to touch the objects. To get the objects in their proper places, the director needed to give instructions to the matcher to move the objects.  For example, the director might say, "take the red box in the top corner and move it down to the very bottom row," and the matcher would then perform the action.  The matcher's eye movements were tracked as they listened to and interpreted the director's instructions. 

To investigate perspective taking, the instructions given by the director were actually scripted beforehand in order to create certain ambiguities. Most of the objects in the grid, such as the red box, were mutually visible to both participants (i.e., visible from both sides of the grid).  However, some of objects, like the brush and the green candle, were occluded from the director's view; the matcher could see them, but had no reason to believe that the director knew the contents of these occluded squares, and thus had no reason to expect her to ever refer to them. However, sometimes the director would refer to a mutually visible object using a description that also happened to match one of the hidden objects.  For instance, the director might instruct the matcher to "pick up the small candle." Note that for the director, the small candle is the purple candle. A given matcher would see this grid in one of two conditions: In the **Experimental** condition, the matcher saw an additional green candle in a hidden box that was even smaller than the purple candle (see middle panel of the above figure).  This object was called a "competitor" because it matched the description of the intended referent (the purple candle). In the **Baseline** condition, the green candle was replaced with an object that did not match the director's description, such as an apple. These ambiguous situations provided the main data for the experiment, and in total there were eight different grids in the experiment that presented analogous situations to the example above. 

<a href="https://journals.sagepub.com/doi/abs/10.1111/1467-9280.00211", target = "_blank">A previous eye-tracking study by the same authors</a> had found the presence of the competitors severely confused the matchers, suggesting that people were surprisingly egocentric---they found it hard to ignore "privileged" information when interpreting another person's speech. For example, when the director said to "pick up the small candle," they spent far more time looking at a hidden green candle than a hidden apple, even though neither one of these objects, being hidden, was a viable referent.  We refer to the difference in looking time as the 'egocentric interference effect'.

Experiment 2 by Keysar, Lin, and Barr aimed to follow up on this finding. In the previous article, the matcher had reason to believe that the director was merely ignorant of the identity of the hidden objects. But what would happen if the matcher was given reason to believe that the director actually had a **false belief** about the hidden object?  For example, would the matcher experience less egocentric interference if he or she had reason to think that the director thought that the hidden candle was a toy truck?

To test this, half of the participants were randomly assigned to a **false belief** condition, where the matcher was led to believe that the director had a false belief about the identity of the hidden object; the other half participated in the **ignorance** condition, where as in previous experiments, they were led to believe that the director simply did not know what was in the hidden squares.

There were 40 participants in this study, 20 in the false belief condition, and 20 in the ignorance condition. There were also an equal number of male and female participants in the study. To spoil the plot a bit, Keysar, Lin and Barr did not find any effect of condition on looking time. However, they did not consider sex as a potential moderating variable. Thus, we will explore the effects of ignorance vs. false belief on egocentric interference, broken down by the sex of the matcher.

## Before starting lets check:

1. The `.csv` file is saved into a folder on your computer and you have manually set this folder as your working directory. 

2. The `.Rmd` file is saved in the same folder as the `.csv` files. For assessments we ask that you save it with the format `GUID_Level2_Semester2_Lab4.Rmd` where `GUID` is replaced with your `GUID`. Though this is a formative assessment, it may be good practice to do the same here.

## The Data
## Task 1A: Libraries

* In today's assignment you will need both the `tidyverse` and `ez` packages. Enter code into the t1A code chunk below to load in both of these libraries.

```{r t1A, message = FALSE, warning=FALSE}
# load in the packages
```

## Task 1B: Loading in the data

* Use `read_csv()` to replace the `NULL` in the t1B code chunk below to load in the data stored in the datafile `keysar_lin_barr_2003.csv`. Store the data in the variable `dat`. Do not change the filename of the datafile. 

```{r t1B, warning=FALSE, message = FALSE}
dat <- NULL
```

Take a look at your data (`dat`) in the console using `glimpse()` or `View()`, or just display it by typing in the name. You will see the following columns:

|variable   |description|
|-----------|-----------|
|`subject`  |unique identifier for each subject|
|`sex`      |whether the subject was male or female|
|`condition`|what condition the subject was in|
|`looktime` |egocentric interference|

We have simplified things from the original experiment by collapsing the baseline vs. experimental conditions into a single DV.  Our DV, egocentric interference, is the average difference in looking time for each subject (in milliseconds per trial) for hidden competitors (e.g., small candle) versus hidden noncompetitors (e.g., apple). The larger this number, the more egocentric interference the subject experienced.

## Task 2: Calculate cell means

Today we are going to focus on just the main analysis and write-up, and not the assumptions, but as always before running any analysis you should check that your assumptions hold.

One of the elements we will need for our write-up is some descriptives. We want to start by creating some summary statistics for the four conditions. Remember, two factors (sex, condition) with 2 levels each (sex: female vs male; condition: false belief vs ignorance) will give four conditions, and as such in our summary table, four cells created by factorially combining sex and condition. 

* Replace the NULL in the `t2` code chunk below to create the four cells created by factorially combining sex and condition, summarising the mean and standard deviation for each cell.
    - Store the descriptives in the tibble `cell_means`
    - Call the column for the mean `m` and the column for the standard deviation `sd`.
    - Your table should have four rows and four columns as shown on Moodle but with your values replacing the XXs
    - Follow the case and spelling *exactly*.

```{r t2}
cell_means <- NULL
```

## Task 3: Marginal means for sex

We will also need to have some descriptives where we just look at the means of a given factor; the marginal means - the means of the levels of one factor regardless of the other factor.

* Replace the NULL in the `t3` code chunk below to calculate the marginal means and standard deviations for the factor, sex. 
    - Store these descriptives in the tibble `marg_sex`
    - Call the column for the mean `m` and the column for the standard deviation `sd`. 
    - Your table should have two rows and three columns as shown on Moodle but with your values replacing the XXs
    - Follow the case and spelling *exactly*.

```{r t3}
marg_sex <- NULL
```

## Task 4: Marginal means for condition

And now do the same for condition. 

* Replace the NULL in the `t4` code chunk below to calculate the marginal means and standard deviations for the factor, condition 
    - Store these descriptives in the tibble `marg_cond`
    - Call the column for the mean `m` and the column for the standard deviation `sd`. 
    - Your table should have two rows and three columns as shown on Moodle but with your values replacing the XXs
    - Follow the case and spelling *exactly*

```{r t4}
marg_cond <- NULL
```

## Task 5: Interaction plot

And finally we are going to need a plot.  When you have two factors, you want to show both factors on the plot to give the reader as much information as possible and save on figure space.  The best way to do this is through some sort of interaction plot as shown in the lab.  It is really a lot easier than it looks and just requires you to think about setting the aes by the different conditions.

* Insert code into the `t5` code chunk below to replicate the figure shown to you on Moodle
    - Pay particular attention to labels, axes dimensions, color and background. 
    - Note that the figure must appear when your code is knitted.
    
* **Note:** The figure in the activity is a nice figure but should really have error bars on it if I was including it in an actual paper. Including the error bars may help in clarifying the descriptive statistics as you would see as although the means are different, there is huge overlap in terms of error bars.

```{r t5}
# to do: something with ggplot to replicate the figure


```

## Task 6: Recap Question 1

Thinking about the above information, one of the below statements would be an acceptable hypothesis for the interaction effect of sex and condition, but which one:

* In the `t6` code chunk below, replace the `NULL` with the number of the statement below that best summarises this analysis. Store this single value in `answer_t6`

1. We hypothesised that there will be a significant difference between males and females in egocentric interference (mean looking time (msecs)) regardless of condition.
2. We hypothesised that there will be a significant difference between participants in the false belief condition and those in the ignorance condition in terms of egocentric interference (mean looking time (msecs)) regardless of sex of participant.
3. We hypothesised that there would be a significant interaction between condition and sex of participant on egocentric interference (mean looking time (msecs))
4. We hypothesised that there will be no significant difference between males and females in egocentric interference (mean looking time (msecs)) regardless of condition but that there would be a significant difference between participants in the false belief condition and those in the ignorance condition in terms of egocentric interference (mean looking time (msecs)) regardless of sex of participant.

```{r t6}
answer_t6 <- NULL
```

## Task 7: Recap Question 2

Thinking about the above information, one of the below statements is a good description of the marginal means for sex, but which one:

* In the `t7` code chunk below, replace the `NULL` with the number of the statement below that best summarises this analysis. Store this single value in `answer_t7`

1. The female participants have an average longer looking time (M = 777.98, SD = 911.53) than the male participants (M = 555.04, SD = 707.81) which may suggest a significant main effect of sex
2. The female participants have an average shorter looking time (M = 777.98, SD = 911.53) than the male participants (M = 555.04, SD = 707.81) which may suggest a significant main effect of condition
3. The female participants have an average shorter looking time (M = 777.98, SD = 911.53) than the male participants (M = 555.04, SD = 707.81) which may suggest a significant main effect of sex
4. The female participants have an average longer looking time (M = 777.98, SD = 911.53) than the male participants (M = 555.04, SD = 707.81) which may suggest a significant main effect of condition

```{r t7}
answer_t7 <- NULL
```

## Task 8: Recap Question 3

Thinking about the above information, one of the below statements is a good description of the marginal means for condition, but which one:

* In the `t8` code chunk below, replace the `NULL` with the number of the statement below that best summarises this analysis. Store this single value in `answer_t8`

1. The participants in the false belief group had an average longer looking time (M = 549.58, SD = 775.91) than the participants in the ignorance group (M = 749.58, SD = 861.23) which may suggest a significant main effect of condition.
2. The participants in the false belief group had an average shorter looking time (M = 549.58, SD = 775.91) than the participants in the ignorance group (M = 749.58, SD = 861.23) which may suggest a significant main effect of condition.
1. The participants in the false belief group had an average longer looking time (M = 549.58, SD = 775.91) than the participants in the ignorance group (M = 749.58, SD = 861.23) which may suggest a significant main effect of sex.
2. The participants in the false belief group had an average shorter looking time (M = 549.58, SD = 775.91) than the participants in the ignorance group (M = 749.58, SD = 861.23) which may suggest a significant main effect of sex.

```{r t8}
answer_t8 <- NULL
```

## Task 9: Running the factorial ANOVA

Great, so we have looked at our descriptives and thought about what effects there might be.  What we need to do now is run the ANOVA using the `ezANOVA()` function. The ANOVA we are going to run is a two-way between-subjects ANOVA because both conditions are between-subjects variables. You may need to refer back to the lab or to have a look at the help on `ezANOVA()` to see how to add a second variable/factor. 

* Replace the NULL in the `t9` code chunk below to run this two-way between-subjects ANOVA. 
    - Look at the inclass for guidance. You need the data, the dv, the two between condition, and the participant id.
    - Do not `tidy()` the output. Do nothing to the output other than store it in the variable named `mod` (note: technically it will store as a list).
    - The code will convert the condition and participant ids to factors automatically. This is fine.

```{r t9}
mod <- NULL
```

# Task 10: Interpreting the ANOVA output Question

Thinking about the above information, one of the below statements is a good summary of the outcome ANOVA, but which one:

* In the `t10` code chunk below, replace the `NULL` with the number of the statement below that best summarises this analysis. Store this single value in `answer_t10`

1. There is a significant main effect of sex, but no main effect of condition and no interaction betwen condition and sex.
2. There is a significant main effect of condition, but no main effect of sex and no interaction betwen condition and sex.
3. There is no significant main effect of sex or condition and there is no significant interaction between condition and sex.
4. There is a significant main effect of sex, a significant main effect of condition, and a significant interaction between condition and sex

```{r t10}
answer_t10 <- NULL
```

## Task 11: Report your results

Write a paragraph reporting your findings.  *NOTE:* You can use inline code to report the $F$ values, but note that you cannot use `broom::tidy()` for objects created by `ezANOVA()`. Here is a hint: `mod$ANOVA` gives you a table of your results (`ezANOVA()` returns a list with two elements; `mod$ANOVA` returns the element of the list called `ANOVA` that has the results). You can `pull()` and `pluck()` whatever you need from this table.

<!-- start of results: don't delete this line -->

Write your summary between these two green lines

<!-- end of results: don't delete this line -->

# Finished

Well done, you are finshed! Now you should go check your answers against the solution file which can be found on Moodle. You are looking to check that the resulting output from the answers that you have submitted are exactly the same as the output in the solution - for example, remember that a single value is not the same as a coded answer. Where there are alternative answers it means that you could have submitted any one of the options as they should all return the same answer. If you have any questions please post them on the moodle forum or on the <a href = "https://rguppies.slack.com", target = "_blank">rguppies.slack.com</a> forum **#level2_2018**.

See you in the next lab!