## Practice Your Skills

This activity uses open data from Experiment 1 of <a href="https://journals.sagepub.com/stoken/default+domain/d5HcBHg85XamSXGdYqYN/full" target = "_blank">Mehr, Song, and Spelke (2016)</a>. This exercise is taken from the <a href="https://sites.google.com/view/openstatslab/home?authuser=0" target = "_blank">Open Stats Lab at Trinity University, US</a>.

In order to complete these tasks you will need to download the data .csv file and the .Rmd file, which you need to edit, titled `Ch5_PracticeSkills_Template.Rmd`. These can be downloaded within a zip file from the link below. Once downloaded and unzipped, you should create a new folder that you will use as your working directory; put the data file and the .Rmd file in that folder and set your working directory to that folder through the drop-down menus at the top. [**Download the Exercises .zip file from here**](data/06-s01/Ch5_PracticeSkills.zip).

Now open the .Rmd file within RStudio. You will see there is a code chunk for each task. Follow the instructions on what to edit in each code chunk. The exercises in this section will guide you to do some data wrangling, run One-Sample t-tests on published data, and visualise data. Thus, you can check the published paper to see if you were able to replicate their results.  

### Does Music Convey Social Information to Infants? 

Parents often sing to their children and, even as infants, children listen to and look at their parents while they are singing. Research by Mehr, Song, and Spelke (2016) sought to explore the psychological function that music has for parents and infants, by examining the hypothesis that particular melodies convey important social information to infants. Specifically, melodies convey information about social affiliation.

The authors argue that melodies are shared within social groups. Whereas children growing up in one
culture may be exposed to certain songs as infants (e.g., “Rock-a-bye Baby”), children growing up in
other cultures (or even other groups within a culture) may be exposed to different songs. Thus, when a novel person (someone who the infant has never seen before) sings a familiar song, it may signal to the infant that this new person is a member of their social group.

To test this hypothesis, the researchers recruited 32 infants and their parents to complete an
experiment. During their first visit to the lab, the parents were taught a new lullaby (one that neither they nor their infants had heard before). The experimenters asked the parents to sing the new lullaby to their child every day for the next 1-2 weeks.

Following this 1-2 week exposure period, the parents and their infant returned to the lab to complete
the experimental portion of the study. Infants were first shown a screen with side-by-side videos of
two unfamiliar people, each of whom were silently smiling and looking at the infant. The researchers
recorded the looking behavior (or gaze) of the infants during this ‘baseline’ phase. Next, one by one, the two unfamiliar people on the screen sang either the lullaby that the parents learned or a different lullaby (that had the same lyrics and rhythm, but a different melody). Finally, the infants saw the same silent video used at baseline, and the researchers again recorded the looking behavior of the infants during this ‘test’ phase. For more details on the experiment’s methods, please refer to Mehr et al. (2016) Experiment 1.

For the exercise here we will be looking at the baseline data and test trial data for gazing proportion specifically.


**Before starting let's check:**

1. The `.csv` file is saved into a folder on your computer and you have manually set this folder as your working directory. 

2. The `.Rmd` file is saved in the same folder as the `.csv` files.


### Load in the data {#Ch5PracticeSkillsT0}

Call `tidyverse` to the `library()` and load in the data (`socialmelodies_exp1.csv`) and store them in object `melodydata`.

```{r libraries, echo = TRUE, warning=FALSE, message=FALSE, eval = FALSE}
library("tidyverse")

melodydata <- NULL
```


**View the data**

1. It is always a good idea to familiarise yourself with the layout of the data that you have just loaded in. You can do this through using `glimpse()` or `View()` in the Console window. Note, you will not analyse all of these variables. Try to find the variables that are relevant to the study description above. 


**The Tasks:**

Now that we have the data loaded, tidyverse attached, and have viewed our data, you should now try to complete the following tasks. Go through the tasks and change only the `NULL` with what the question asks for and then make sure that the file `knits` at the end so that you have a fully reproducible code.

### Task 1 - Filter data {#Ch5PracticeSkillsT1}

This data file includes the variables for all 5 experiments reported in the paper. We only want
to analyze the data for Experiment 1. Using the `filter()` function, create a new data frame `melodydata_exp1` that only contains data of Experiment 1 (variable `exp1` with value 1 indicates all data fro Experiment 1). Hint: The new data frame should have 32 observations.

```{r T1, eval = FALSE}
melodydata_exp1 <- NULL
```

### Task 2 - Select data {#Ch5PracticeSkillsT2}

As noted above, we will not be using all variables from `melodydata_exp1` and in order to get a better overview of the variables we are particularly interested in, we want to create an object that only contains the variables we are focusing on here.

Some context:
* First, you want to show that infants' looking behavior did not differ from chance during the
baseline trial (`Baseline_Proportion_Gaze_to_Singer`). In other words, the infants did not show an attentional bias prior to hearing the unfamiliar others sign the song. 
* Second, you want to examine whether the proportion of infants' looking
behaviour toward the singer of the familiar melody (`Test_Proportion_Gaze_to_Singer`) was higher than chance at the test phase.

Thus, create a new data frame called `melodydata_exp1_reduced` that only contains the variables `id`, `Baseline_Proportion_Gaze_to_Singer`, and `Test_Proportion_Gaze_to_Singer`. 

Hint: The new data frame contains 32 observations and 3 variables.

```{r T2, eval = FALSE}
melodydata_exp1_reduced <- NULL
```


### Task 3 - Testing baseline gazing proportion {#Ch5PracticeSkillsT3}

Perform a One-sample t-test to examine whether the proportion of time spent looking at the person singing the familiar song at baseline did not differ from chance (0.5).


```{r T3, eval = FALSE}
t.test(pull(NULL, NULL), mu = NULL)
```

### Task 4 - Testing test trial gazing proportion {#Ch5PracticeSkillsT4}

Now, perform a One-sample t-test to examine whether the proportion of infants' looking
behaviour toward the singer of the familiar melody was higher than chance at the test phase
(0.5).


```{r T4, eval = FALSE}
t.test(pull(NULL, NULL), mu = NULL)
```

### Task 5 - Gathering data into a different format {#Ch5PracticeSkillsT5}

We want to create a boxplot to depict the proportion of time infants spent looking at the singer of the familiar song at the baseline and test trials. However, before we can do that, we need to slightly change the format of our `melodydata_exp1_reduced` data frame: Because we need to represent the same cases (individuals) twice in the same figure, we need to reorganise the data so it has all of the gaze proportions as one variable (`Proportion`), but with a separate variable indicating whether it belongs to the baseline or test trial (`TrialType`). Put differently, each participant should be represented by two rows; one row with the baseline proportion and another row with the test trial proportion.

Store the new data frame in object `melodydata_exp1_wide`.

Hint: You will need `pivot_longer` function for this step.
Hint: The new data frame has 64 observations and 3 variables (`id`, `TrialType`, `Proportion`).


```{r T5, eval = FALSE}
melodydata_exp1_wide <- melodydata_exp1_reduced %>% 
  pivot_longer(cols = NULL,
               names_to = NULL,
               values_to = NULL)
```



### Task 6 - Visualise baseline and test trial data {#Ch5PracticeSkillsT6}

Generate a boxplot to depict the proportion of time infants spent looking at the singer of the
familiar song at the baseline and test trials.

* Turn off the legend using the `guides()` as it isn't needed because the x-axis tells you which trial is which. 

```{r T6, eval = FALSE}
ggplot(NULL)

```

### Task 7 - Compare your analyses with the analyses reported in the published paper {#Ch5PracticeSkillsT7}

Finally, check the results section for Experiment 1 in the published paper and compare the results from your analyses with the ones reported in the paper: <a href="https://journals.sagepub.com/stoken/default+domain/d5HcBHg85XamSXGdYqYN/full" target = "_blank">Mehr, Song, and Spelke (2016)</a>. What do you find?


Well done, you are finished! Make sure to `knit` this `.Rmd` file. You have successfully replicated analyses and data visualisation from a published paper. Check your answers against the solutions at the end of the chapter, too.
