## Solutions to Questions

```{r lab6-solutions-setup, echo=FALSE, message=FALSE, warning=FALSE}

```


### The Two-Sample t-test

#### Task 1
```{r inclass-hidden solution, warning = FALSE, echo = FALSE, message = FALSE, include = FALSE}

## TASK 1
evaluators <- read_csv("data/06-s01/inclass/evaluators.csv")

e_agg <- evaluators %>%
  summarize(mean_age = mean(age, na.rm = TRUE),
            sd_age = sd(age, na.rm = TRUE))

e_count <- evaluators %>%
  count(sex)

# If using `recode()`:
e_count <- evaluators %>%
  count(sex) %>%
  mutate(sex_names = recode(sex, "1" = "male", "2" = "female"))

## TASK 2
# 1. load in the data
ratings <- read_csv("data/06-s01/inclass/ratings.csv")

# 2. first step: pull out the ratings associated with intellect
iratings <- ratings %>%
  filter(Category %in% c("competent", "thoughtful", "intelligent"))

# second step: calculate means for each evaluator
imeans <- iratings %>%
  group_by(eval_id) %>%
  summarise(Rating = mean(Rating))

# 3. add Category variable 
# this way we can combine with 'impression' and 'hire' into a single table, very useful!
imeans2 <- imeans %>%
  mutate(Category = "intellect")

# 4. & 5. combine into a single table
ratings2 <- ratings %>%
  filter(Category %in% c("impression", "hire")) %>%
  bind_rows(imeans2) %>%
  inner_join(evaluators, "eval_id") %>%
  select(-age, -sex) %>%
  arrange(eval_id, Category)
```


```{r Ch6InClassQueT1-hidden, message = FALSE, eval = FALSE}
library("tidyverse")
library("broom") # you'll need broom::tidy() later

evaluators <- read_csv("evaluators.csv")

evaluators %>%
  summarize(mean_age = mean(age, na.rm = TRUE))

evaluators %>%
  count(sex)

# If using `recode()`:
evaluators %>%
  count(sex) %>%
  mutate(sex_names = recode(sex, "1" = "male", "2" = "female"))

```

* The mean age of the evaluators was `r e_agg %>% pull(mean_age) %>% round(1)`
* The standard deviatoin of the age of the evaluators was `r e_agg %>% pull(sd_age) %>% round(2)`
* There were `r e_count %>% filter(sex_names == "male") %>% pull(n)` males and `e_count %>% filter(sex_names == "female") %>% pull(n)` females, with `r e_count %>% filter(is.na(sex_names)) %>% pull(n)` people not stating a sex.


[Return to Task](#Ch6InClassQueT1)

#### Task 2

* load in the data
```{r Ch6InClassQueT2-1, eval = FALSE, message = FALSE}

ratings <- read_csv("ratings.csv")
```

1. First pull out the ratings associated with intellect
```{r Ch6InClassQueT2-2, eval = FALSE, message = FALSE}
iratings <- ratings %>%
  filter(Category %in% c("competent", "thoughtful", "intelligent"))
```

2. Next calculate means for each evaluator
```{r Ch6InClassQueT2-3, eval = FALSE, message = FALSE}
imeans <- iratings %>%
  group_by(eval_id) %>%
  summarise(Rating = mean(Rating))
```

3. Mutate on the Category variable. This way we can combine with 'impression' and 'hire' into a single table which will be very useful!
```{r Ch6InClassQueT2-4, eval = FALSE, message = FALSE}
imeans2 <- imeans %>%
  mutate(Category = "intellect")
```

And then combine all the information in to one single tibble.
```{r Ch6InClassQueT2-5, eval = FALSE, message = FALSE}
ratings2 <- ratings %>%
  filter(Category %in% c("impression", "hire")) %>%
  bind_rows(imeans2) %>%
  inner_join(evaluators, "eval_id") %>%
  select(-age, -sex) %>%
  arrange(eval_id, Category)
```

[Return to Task](#Ch6InClassQueT3)

#### Task 4

1. First we calculate the group means:

```{r ch6-task4-steps1_sol, echo = TRUE, eval = TRUE, results="hide"}
group_means <- ratings2 %>%
  group_by(condition, Category) %>%
  summarise(m = mean(Rating), sd = sd(Rating))
```

2. And we can call them and look at them by typing:
```{r ch6-task4-steps2_sol, echo = TRUE, eval = TRUE, results="hide", warning = FALSE}
group_means
```

3. Now to just look at intellect ratings we need to filter them into a new tibble:
```{r ch6-task4-steps3_sol, echo = TRUE, eval = TRUE, results="hide"}
intellect <- filter(ratings2, Category == "intellect")
```

4. And then we run the actual t-test and tidy it into a table.
    * `t.test()` requires two vectors as input
    * `pull()` will pull out a single column from a tibble, e.g. Rating from intellect
    * `tidy()` takes information from a test and turns it into a table. Try running the t.test with and without piping into `tidy()` to see what it does differently.
 
```{r ch6-task4-steps4_sol, echo = TRUE, eval = FALSE, results="hide"}
intellect_t <- t.test(intellect %>% filter(condition == "listened") %>% pull(Rating),
                      intellect %>% filter(condition == "read") %>% pull(Rating),
                      var.equal = TRUE) %>%
  tidy()
```

5. Now we repeat for HIRE and IMPRESSION
```{r ch6-task4-steps5_sol, echo = TRUE, eval = FALSE, results="hide"}
hire <- filter(ratings2, Category == "hire")
hire_t <- t.test(hire %>% filter(condition == "listened") %>% pull(Rating),
                      hire %>% filter(condition == "read") %>% pull(Rating),
                 var.equal = TRUE) %>%
  tidy()
```

6. And for Impression
```{r ch6-task4-steps6_sol, echo = TRUE, eval = FALSE, results="hide"}
impress <- filter(ratings2, Category == "impression")
impress_t <- t.test(impress %>% filter(condition == "listened") %>% pull(Rating),
                    impress %>% filter(condition == "read") %>% pull(Rating),
                    var.equal = TRUE) %>%
  tidy()
```

7. Before combining all into one table showing all three t-tests
```{r ch6-task4-steps7_sol, echo = TRUE, eval = FALSE, results="hide", warning = FALSE}
results <- bind_rows("hire" = hire_t, 
                     "impression" = impress_t,
                     "intellect" = intellect_t, .id = "id")

results
```

[Return to Task](#Ch6InClassQueT4)


### Practice Your Skills

#### Task 1A: Libraries

```{r t1A, eval = FALSE, message = FALSE}
library(broom)
library(tidyverse)
```

[Return to Task](#Ch6AssignQueT1)

#### Task 1B: Loading in the data

* Use `read_csv()` to read in data!

```{r lab6-hml-t1b, message = FALSE}
crt <- read_csv("data/06-s01/homework/CRT_Data.csv")
```

```{r t1B, message = FALSE, eval = FALSE}
crt <- read_csv("CRT_Data.csv")
```

[Return to Task](#Ch6AssignQueT1)

#### Task 2: Selecting only relevant columns

The key columns are:

* ID
* Treatment
* CorrectAnswers

Creating `crt2` which is a tibble with 3 columns and 243 rows.

```{r t2}
crt2 <- select(crt, ID, Treatment, CorrectAnswers)
```

[Return to Task](#Ch6AssignQueT2)

#### Task 3: Verify the number of subjects in each group

The Participants section of the article contains the following statement:

**243 men (mostly college students; for demographic details, see Table S1 in the Supplemental Material available online) were randomly administered a topical gel containing either testosterone (n = 125) or placebo (n = 118).**

In the t3 code block below, replace the `NULLs` with lines of code to calculate:

1. The number of men in each Treatment. This should be a tibble/table called `cond_counts` containing a column called `Treatment` showing the two groups and a column called `n` which shows the number of men in each group.

2. The total number of men in the sample. This should be a single value, not a tibble/table, and should be stored in `n_men`. 

You know the answer to both of these tasks already. Make sure that your code gives the correct answer!

For `cond_counts`, you could do:

```{r t3-1}
cond_counts <- crt2 %>% group_by(Treatment) %>% summarise(n = n())
```
Or alternatively
```{r t3-2}
cond_counts <- crt2 %>% count(Treatment)
```

For `n_men`, you could do:
```{r t3-3}
n_men <- crt2 %>% summarise(n = n()) %>% pull(n)
```
Or alternatively
```{r t3-4}
n_men <- nrow(crt2)
```

**Solution:**

When formatted with inline R code as below:

**`r backtick("r n_men")` men (mostly college students; for demographic details, see Table S1 in the Supplemental Material available online) were randomly administered a topical gel containing either testosterone (n = `r backtick("r cond_counts %>% filter(Treatment == 1) %>% pull(n)")`) or placebo (n = `r backtick("r cond_counts %>% filter(Treatment == 0) %>% pull(n)")`).**

should give:

**`r n_men` men (mostly college students; for demographic details, see Table S1 in the Supplemental Material available online) were randomly administered a topical gel containing either testosterone (n = `r cond_counts %>% filter(Treatment == 1) %>% pull(n)`) or placebo (n = `r cond_counts %>% filter(Treatment == 0) %>% pull(n)`).**

[Return to Task](#Ch6AssignQueT3)

#### Task 4: Reproduce Figure 2A

You could produce a good representation of Figure 2A with the following approach:

```{r t4, fig.cap='A representation of Figure 2A'}
crt_means <- crt2 %>% 
  group_by(Treatment) %>% 
  summarise(m = mean(CorrectAnswers), sd = sd(CorrectAnswers)) %>%
  mutate(Treatment = recode(Treatment, "0" = "Placebo", "1" = "Testosterone Group"))

ggplot(crt_means, aes(Treatment, m, fill = Treatment)) + 
  geom_col() + 
  theme_classic() + 
  labs(x = "CRT", y = "Number of Correct Answers") +
  guides(fill = "none") +
  scale_fill_manual(values = c("#EEEEEE","#AAAAAA")) +
  coord_cartesian(ylim = c(1.4,2.4), expand = TRUE)

```

[Return to Task](#Ch6AssignQueT4)

#### Task 5: Interpreting your Figure

Option 3 is the correct answer given that:

The Testosterone group (M = 1.66, SD = 1.18) would appear to have fewer correct answers on average than the Placebo group (M = 2.10, SD = 1.02) on the Cognitive Reflection Test suggesting that testosterone does in fact inhibit the ability to override incorrect intuitive judgements with the correct response. 


```{r t5}
answer_t5 <- 3
```

[Return to Task](#Ch6AssignQueT5)

#### Task 6: t-test

You need to pay attention to the order when using this first approach, making sure that the **0** group are entered first. This will put the Placebo groups as Estimate1 in the output. In reality it does not change the values, but the key thing is that if you were to pass this code on to someone, and they expect Placebo to be Estimate1, then you need to make sure you coded it that way.

```{r t6-option1, eval = FALSE}
t_table <- t.test(crt2 %>% filter(Treatment == 0) %>% pull(CorrectAnswers),
                  crt2 %>% filter(Treatment == 1) %>% pull(CorrectAnswers),
                  var.equal = TRUE) %>%
  tidy()
```

* Alternatively, you could use what is known as the formula approach as shown below. Here you state the `DV ~ IV` and you say the name of the tibble in `data = ...`. You just need to make sure that the columns you state as the DV and the IV are actually in the tibble!

```{r t6-option2, eval = FALSE}
t_table <- t.test(CorrectAnswers ~ Treatment, data = crt2, var.equal = TRUE) %>% tidy()
```

Note that this approach will compare based on the alphabetical or numerical order of the values in the independent variable. Therefore, the **0** group would still be the first group in the comparison, matching the previous approach. 

[Return to Task](#Ch6AssignQueT6)

#### Task 7: Reporting results

* The degrees of freedom (df) is found under `parameter`
```{r t7A, eval = FALSE}
t_df <- t_table$parameter
```

* An alternative option for this would be as follows, using the `pull()` method. This would work for B to D as well

```{r t7A-1, eval = FALSE}
t_df <- t_table %>% pull(parameter)
```


* The t-value is found under `statistic`
```{r t7B, eval = FALSE}
t_value <- t_table$statistic %>% round(3)
```

* The p-value is found under `p.value`
```{r t7C, eval = FALSE}
p_value <- t_table$p.value %>% round(3)
```

* The absolute difference between the two means can be calculated as follows:
```{r t7D, eval = FALSE}
t_diff <- (t_table$estimate1 - t_table$estimate2) %>% round(3) %>% abs()
```

If you have completed t7A to t7D accurately, then when knitted, Option 4 would be stated as such

**The testosterone group performed significantly worse (0.438 fewer correct answers) than the placebo group, t(241) = 3.074, p = 0.002**

and would therefore be the correct answer! 

```{r t7E}
answer_t7e <- 4
```

[Return to Task](#Ch6AssignQueT7)

<span style="font-size: 22px; font-weight: bold; color: var(--purple);">Chapter Complete!</span>
